Discrepancy, Coresets, and Sketches in Machine Learning

### 2019-01-31 komlos.tex
small edits

\begin{abstract}
This paper defines the notion of class discrepancy for families of functions.  It shows that low discrepancy classes admit small offline and streaming coresets. We provide general techniques for bounding the class discrepancy of machine learning problems and specifically do so for matrix covariance approximation, logistic regression, kernel density and any analytic function of the dot product or the squared distance.
Our result resolves a long standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
We provide two more related but independent results. 
First, an exponential improvement of the widely used merge-and-reduce trick which gives improved streaming sketches for any low discrepancy problem.
Second, an extremely simple algorithm for finding low discrepancy sequences (and therefore coresets) for any positive semi-definite kernel. 
This paper establishes some explicit connections between low class discrepancy, coreset complexity, learnability, and streaming algorithms. 
\end{abstract}

\section{Introduction}
The study of coresets in optimization as a whole and in machine learning specifically has a long history. 
The basic setup is as follows.
Suppose you are trying to optimize an expression over a set of items, data points, or examples.
%The optimization problem is difficult and often exponential in the input set size.
The optimization problem is difficult and often square, cubic or even exponential in the input set size.
Therefore, there is a strong incentive to reduce the cardinality of that set. 
The goal is, therefore, to pinpoint a small subset of the data items which approximates the entire input set with respect to some function or geometric measure. Such small sets are called coresets. 
This idea is very general and applies to geometric properties of the data \cite{agarwal2005geometric}, 
clustering \cite{DBLP:conf/compgeom/Har-PeledK05} \cite{DBLP:conf/stoc/FeldmanL11}, classification \cite{DBLP:conf/ijcai/Har-PeledRZ07}, regression \cite{DBLP:conf/nips/MunteanuSSW18} 
machine learning \cite{bachem2017practical}, density estimation \cite{DBLP:journals/corr/abs-1802-01751}, and many other problems.

Obtaining small coresets and understanding the coreset complexity of different problems is of significant theoretical and practical importance.
While some problems obviously do not admit small coresets, other do. 
There are several results that connect the simplicity of the measure and its coreset complexity (the size of the minimal coreset).
In this manuscript, we focus solely on sums of functions applied to the input items.
That is, for $\{x_i,\ldots,x_n\} \subset \X$ we measure $F(q) = \sum_i f(x_i,q)$ for $q \in \Q$ which is either some model parameters or a query.
For example, one could consider the sum of sigmoid activation losses $F(q) = \sum_{i=1}^{n} 1/(1+ \exp(\ip{x_i,q}))$ and $x,q\in \R^d$.
Using Chernoff's inequality and a union bound already shows that sampling $\tilde O(d/\eps^2)$ items give an $\eps n$ approximation to this sum.\footnote{Using $\tilde O(\cdot)$ to suppress poly-logarithmic terms.} 
In general, for families of VC dimension $v$, a sample of $(1/\eps^2)(v+\log(1/\delta))$ suffices \cite{talagrand1994sharper}.
For logistic regression and many other problems $O(d/\eps)$ samples are enough due to fast rate generalization results \cite{van2015fast}.
For Gaussian kernel density, it is known that a sample size of $O(1/\eps^2)$ suffices independently of $d$  \cite{lopez2015towards}.

Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points. A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning. We are not aware of a complete analog to Rademacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size. There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset. However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability. 
%The connection between coresets and discrepancy have been known in the non-streaming setting. For example, \cite{phillips2009small} (Theorem 1.1) provide an analog to our Facts~\ref{fct:eps1},~\ref{fct:eps2}.
The connection between coresets and discrepancy have been known in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.

Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points. Among other applications, this tool is used for outlier detection \cite{schubert2014generalized}, regression \cite{fan2018local}, and clustering \cite{rinaldo2010generalized}. A thorough survey could be found in \cite{silverman2018density}. Given a set of $n$ data points $x_1,\ldots,x_n$ and a query $q$, the density estimate of $q$ is the average $\frac{1}{n} \sum_i K(x_i,q)$ of the kernel evaluations with the data points. The task of finding a coreset for kernel density estimates consists of obtaining a set of points $z_1,\ldots,z_m$ with weights $w_1,\ldots,w_m$ for some $m \ll n$ such that for any query $q$ it holds that 
$\frac{1}{n} \sum_i K(x_i,q) = \frac{1}{m} \sum_i w_i K(z_i,q) \pm \eps$. For this task, the state-of-the-art is given by \cite{DBLP:journals/corr/abs-1802-01751}, achieving $m=\sqrt{d\log(1/\eps)}/\eps$ where $d$ is the dimension of the original data points. Their result holds for any Lipchitz bounded positive semi-definite kernels. The result is constructive though it is polynomial rather than (quasi-)linear in the data size. The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds. Additionally, they provide a simpler algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset. It is in fact known (see \cite{lopez2015towards}, Theorem 1) that a uniform random sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p. $1-\delta$ for some kernel types. 
In this paper we resolve the open question by \cite{DBLP:journals/corr/abs-1802-01751} and prove that the coreset complexity of Gaussian kernel density is indeed $O(\sqrt{d}/\eps)$, matching the lower bound. 
In fact, we show that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = g(\|x-q\|^2)$.
Moreover, we provide a very simple and deterministic algorithm for constructing coresets of size $1/\eps^2$ for any positive kernel.

Logistic Regression is an extremely popular technique for classification. We are given a set of $n$ pairs $x_i,y_i$ with $x_i \in \R^d$ and $y_i \in \{-1,1\}$. The objective is to find a regressor $q \in \R^d$ minimizing the logistic loss defined as $\E_i \log(1+\exp(x_i^\top q y_i))$. A coreset for logistic regression is a set of $m \ll n$ pairs $z_i, v_i$ in $\R^d, \{-1,1\}$ correspondingly along with weights $w_i$, with the property that for any regressor $q$, either $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) \pm \eps$ or $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) (1 \pm \eps)$. A recent paper \cite{DBLP:journals/corr/abs-1805-08571} provides a coreset with a multiplicative guarantee that is based on an average sensitivity property of the dataset. They provide a lower bound for the size of a multiplicative coreset showing that in general it is not possible to achieve $m \ll n$. The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is complexity measure of the dataset.  \cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization. The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.  Our results mentioned above prove that for an additive guarantee, it is possible to obtain a coreset of size $O(\sqrt{d}/\eps)$.

@@

\subsection{Class Discrepancy}
We begin by giving three equivalent definitions of complexity based on discrepancy for sets, functions, and function families. We will use all three interchangeably throughout the manuscript.

@@

\begin{definition} [\bf Coreset Complexity] 
For a function $f:\X,\Q\rightarrow \R$ let $F(q) = \sum_{i=1}^{m} f(x_i,q)$ for a any set $\{x_1,\ldots,x_m\} \subset \X$.
For a set $S \subset [m]$ let $\tilde F(q) = \sum_{i \in S}w_i f(x_i,q)$ for some $w\in\R_+^m$ which is independent of $q$.
The coreset complexity of $f$ is the size of the smallest set $S$ such that $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$.
\end{definition}
\noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$. Although they were previously known (see e.g., \cite{phillips2009small}, Theorem 1.1) we give their proof here for completeness.
\begin{fact}\label{fct:eps1}
Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $O(c/\eps)$.
%The constant $c$ does not depend on $m$.
\end{fact}
\begin{fact}\label{fct:eps2}
Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
%The constant $c$ does not depend on $m$.
\end{fact}
\begin{proof}
\noindent  Consider the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$. We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$. The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
By Definition we can select signs such that $|E(q)| \le m K_m(f)$.

@@

\begin{lemma}\label{uc}
For any set of vectors $x_i \in \R^d$ with $\|x_i\| \leq 1$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\left\| \sum_i \sigma_i x_i^{\otimes k} \right\|_{T_k} \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$). 
\end{lemma}
\begin{proof}
The proof will use Banaszczyk's theorem \cite{Banaszczyk}. 
Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ when $g$ is i.i.d.\ Gaussian).
Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| \leq 1$. 
Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.

@@

\begin{theorem}\label{analitic1}
Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f = f(\ip{q,x})$, indexed by $\|q\| \leq R$, has class discrepancy $O(\sqrt{d}/m)$. 
\end{theorem}
\begin{proof}
Recall that for analytic functions $f$ we have $\left| \frac{d^k f}{dz^k}(z) \right|  \leq C^{k+1} k! $
for some constant $C$. Considering the taylor expansion of $f$ near zero, for $R < 1/C$ the sum
$ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} \leq C \sum_k  (CR)^k \sqrt{ k\log^3(k)}$
corresponding to Lemma~\ref{lem:komlos anl} converges to a constant. The result follows.
\end{proof}

@@

Lemma~\ref{lem:det compactor} alone already allow us to prove Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21}. 
The algorithms are a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions. The above gives class discrepancy of $1/m$ for quantile approximation.
%Below we generalize this algorithm to any low discrepancy class.
Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21} below generalize this algorithm to any low discrepancy class.

\el{Replace with the above?} \zk{changed `Below we generalize this algorithm to any low discrepancy class.' to the line above. Does that resolve the issue?}
\paragraph{Theorem~\ref{thm:streaming11}}
For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
\begin{proof}
Consider feeding the output of the first compactor into a second one etc. Specifically, we start with a single compactor and open a second once it produced any output, then open a third compactor once the second produced output, etc.
Number the compactors $0,\ldots,H$. The weight of items given to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.

@@

\paragraph{Theorem~\ref{thm:streaming12}} 
Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
$Q_\eps$ is an epsilon net for $f$ on $\Q$. 
The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
%For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
\begin{proof}
We start by describing the algorithm, from the perspective of a compactor of level $h$. The compactor observes an input stream of items with weight $2^h$ and outputs a stream of weight $2^{h+1}$. When created the compactor has a budget of $m_h=m$. Once it outputs items to an output stream for the first time, a new compactor of level $h+1$ is created. We keep track of $H$, the level of the top compactor, that did not yet output any items. When $H$ is updated, compactors of level $h<H$ might restrict their budget. Specifically, for some $H'=H-O(\log\log(n/\delta))$ where we set the constant of the $O()$ term later, a compactor of level $h \leq H'$ sets its buffer size to
$$ m_h = \max\left\{2, \ceil{(2/3)^{h-H'}m} \right\} $$
compactors of level $h >H'$ have a buffer size of $m$. We note that although $n$ is present in the definition of $H'$ we can use a crude upper bound. Given that the dependence is doubly logarithmic the upper bound can be extremely crude. Furthermore, $\delta$ is typically set to be exponentially small, so we ignore this issue.

>>>>

\begin{abstract}
This paper defines the notion of class discrepancy for families of functions.  It shows that low discrepancy classes admit small offline and streaming coresets. We provide general techniques for bounding the class discrepancy of machine learning problems. 
As corollaries of the general technique we bound the discrepancy of logistic regression, sigmoid activation loss, matrix covariance, kernel density and any analytic function of the dot product or the squared distance.
Our result resolves a long standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
We provide two more related but independent results. 
First, an exponential improvement of the widely used merge-and-reduce trick which gives improved streaming sketches for any low discrepancy problem.
Second, an extremely simple deterministic algorithm for finding low discrepancy sequences (and therefore coresets) for any positive semi-definite kernel. 
This paper establishes some explicit connections between class discrepancy, coreset complexity, learnability, and streaming algorithms. 
\end{abstract}

\section{Introduction}
The study of coresets in optimization as a whole and in machine learning specifically has a long history. 
The basic setup is as follows.
Suppose you are trying to optimize an expression over a set of items, data points, or examples.
The optimization problem is difficult and often exponential in the input set size.
Therefore, there is a strong incentive to reduce the cardinality of that set. 
The goal is, therefore, to pinpoint a small subset of the data items which approximates the entire input set with respect to some function or geometric measure. Such small sets are called coresets. 
This idea is very general and applies to geometric properties of the data \cite{agarwal2005geometric}, 
clustering \cite{DBLP:conf/compgeom/Har-PeledK05} \cite{DBLP:conf/stoc/FeldmanL11}, classification \cite{DBLP:conf/ijcai/Har-PeledRZ07}, regression \cite{DBLP:conf/nips/MunteanuSSW18} 
machine learning \cite{bachem2017practical}, density estimation \cite{DBLP:journals/corr/abs-1802-01751}, and many other problems.

Obtaining small coresets and understanding the coreset complexity of different problems is of significant theoretical and practical importance.
While some problems obviously do not admit small coresets, other do. 
There are several results that connect the simplicity of the measure and its coreset complexity (the size of the minimal coreset).
In this manuscript, we focus solely on sums of functions applied to the input items.
That is, for $\{x_i,\ldots,x_n\} \subset \X$ we measure $F(q) = \sum_i f(x_i,q)$ for $q \in \Q$ which is either some model parameters or a query.
For example, one could consider the sum of sigmoid activation losses $F(q) = \sum_{i=1}^{n} 1/(1+ \exp(\ip{x_i,q}))$ and $x,q\in \R^d$.
Using Chernoff's inequality and a union bound already shows that sampling $\tilde O(d/\eps^2)$ items give an $\eps n$ approximation to this sum.\footnote{Using $\tilde O(\cdot)$ to suppress poly-logarithmic terms.} 
In general, for families of VC dimension $v$, a sample of $(v+\log(1/\delta))/\eps^2$ suffices \cite{talagrand1994sharper}.
For logistic regression and many other problems $O(d/\eps)$ samples are enough due to fast rate generalization results \cite{van2015fast}.
For Gaussian kernel density, it is know that a sample size of $O(1/\eps^2)$ suffices independently of $d$.

Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points. A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning. We are not aware of a complete analog to Rademacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size. There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset. However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability. The connection between coresets and discrepancy have been known in the non-streaming setting. For example, \cite{phillips2009small} (Theorem 1.1) provide an analog to our Facts~\ref{fct:eps1},~\ref{fct:eps2}.

Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points. Among other applications, this tool is used for outlier detection \cite{schubert2014generalized}, regression \cite{fan2018local}, and clustering \cite{rinaldo2010generalized}. A thorough survey could be found in \cite{silverman2018density}. Given a set of $n$ data points $\{x_1,\ldots,x_n\}$ and a query $q$, the density estimate of $q$ is the average $\frac{1}{n} \sum_i K(x_i,q)$ of the kernel evaluations with the data points. The task of finding a coreset for kernel density estimates consists of obtaining a set of points $z_1,\ldots,z_m$ with weights $w_1,\ldots,w_m$ for some $m \ll n$ such that for any query $q$ it holds that 
$\frac{1}{n} \sum_i K(x_i,q) = \frac{1}{m} \sum_i w_i K(z_i,q) \pm \eps$. For this task, the state-of-the-art is given by \cite{DBLP:journals/corr/abs-1802-01751}, achieving $m=\sqrt{d\log(1/\eps)}/\eps$ where $d$ is the dimension of the original data points. Their result holds for any Lipchitz bounded positive semi-definite kernels. The result is constructive though it is polynomial rather than (quasi-)linear in the data size. The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds. The authors provide a simple algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset. It is in fact known (see \cite{lopez2015towards}, Theorem 1) that a uniform random sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p. $1-\delta$ for some kernel types. 
In this paper we resolve this question and prove that the coreset complexity of Gaussian kernel density is indeed $O(\sqrt{d}/\eps)$ which matches the lower bound provided by \cite{DBLP:journals/corr/abs-1802-01751}. 
In fact, we should that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = g(\|x-q\|^2)$.
Moreover, we provide a very simple and deterministic algorithm for constructing coresets of size $1/\eps^2$ for any positive kernel.

Logistic Regression is an extremely popular technique for classification. We are given a set of $n$ pairs $x_i,y_i$ with $x_i \in \R^d$ and $y_i \in \{-1,1\}$. The objective is to find a regressor $q \in \R^d$ minimizing the logistic loss defined as $\E_i \log(1+\exp(x_i^\top q y_i))$. A coreset for logistic regression is a set of $m \ll n$ pairs $z_i, v_i$ in $\R^d, \{-1,1\}$ correspondingly along with weights $w_i$, with the property that for any regressor $q$, either $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) \pm \eps$ or $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) (1 \pm \eps)$. A recent paper \cite{DBLP:journals/corr/abs-1805-08571} provides a coreset with a multiplicative guarantee that is based on an average sensitivity property of the dataset. They provide a lower bound for the size of a multiplicative coreset showing that in general it is not possible to achieve $m \ll n$. The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is complexity measure of the dataset.  \cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization. The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.

@@

\subsection{Class Discrepancy}
We begin by giving three equivalent definitions of complexity based on discrepancy for sets, functions, and function families. We will use all three interchangeably throughout the manuscript. 
Our notation is intentionally similar to the definition of the Rademacher complexity for reasons that will become clear later.

@@

\begin{definition} [\bf Coreset Complexity] 
For a function $f:\X,\Q\rightarrow \R$ let $F(q) = \sum_{i=1}^{m} f(x_i,q)$ for a any set $\{x_1,\ldots,x_m\} \subset \X$.
For a set $S \subset [m]$ let $\tilde F(q) = \sum_{i \in S}w_i f(x_i,q)$ for some $w\in\R_+^m$ which is independent of $q$.
The coreset complexity of $f$ is the size of the smallest set $S$ such that $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$.
\end{definition}
\noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
\todo{add citation to jeff's thesis}.
\begin{fact}\label{fct:eps1}
Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $f$ $O(c/\eps)$.
The constant $c$ does not depend on $m$.
\end{fact}
\begin{fact}\label{fct:eps2}
Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
The constant $c$ does not depend on $m$.
\end{fact}
\begin{proof}
\noindent  Consider the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$. We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$. The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
By Definition we can select signs such that $|E(q)| \le m K_m(f)$.

@@

\begin{lemma}\label{uc}
For any set of vectors $x_i \in \R^d$ with $\|x_i\| \leq 1$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\left\| \sum_i \sigma_i x_i^{\otimes k} \right\|_{T_k} \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$). 
\end{lemma}
\begin{proof}
The proof will use Banaszczyk's theorem \cite{Banaszczyk}. 
Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ when $g$ is i.i.d.\ Gaussian).
Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| \leq 1$. 
Then, there exist signs $\sigma$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.

@@

\begin{theorem}\label{analitic1}
Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that functions $f = f(\ip{q,x})$, indexed by $\|q\| \leq R$, have class discrepancy $O(\sqrt{d}/m)$. 
\end{theorem}
\begin{proof}
Recall that for analytic functions $f$ we have $\left| \frac{d^k f}{dz^k}(z) \right|  \leq C^{k+1} k! $
for some constant $C$. Considering the taylor expansion of $f$ near zero, for $R < 1/C$ the sum
$ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} \leq C \sum_k  (CR)^k \sqrt{ k\log^3(k)}$
corresponding to Lemma~\ref{lem:komlos anl} converges to a constant. The result follows.
\end{proof}

@@

Lemma~\ref{lem:det compactor} alone already allow us to prove Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21}. 
The algorithms are a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions. The above gives class discrepancy of $1/m$ for quantile approximation.
Below we generalize this algorithm to any low discrepancy class.

\todo{Replace with the above?}
\paragraph{Theorem~\ref{thm:streaming11}}
For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
\begin{proof}
Consider feeding the output of the first compactor into a second one etc. Specifically, we start with a single compactor and open a second once it produced any output, then open a third compactor once the second produced output, etc.
Number the compactors $0,\ldots,H$. The weight of items given to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.

@@

\paragraph{Theorem~\ref{thm:streaming12}} 
For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
\begin{proof}
We start by describing the algorithm, from the perspective of a compactor of level $h$. The compactor observes an input stream of items with weight $2^h$ and outputs a stream of weight $2^{h+1}$. When created the compactor has a budget of $m_h=m$. Once it outputs items to an output stream for the first time, a new compactor of level $h+1$ is created. We keep track of $H$, the level of the top compactor, that did not yet output any items. When $H$ is updated, compactors of level $h<H$ might restrict their budget. Specifically, for some $H'=H-O(\log\log(n/\delta))$ where we set the constant of the $O()$ term later, a compactor of level $h \leq H'$ sets its buffer size to
$$ m_h = \max\left\{2, \ceil{(2/3)^{h-H'}m} \right\} $$
compactors of level $h >H'$ have a buffer size of $m$. We note that although $n$ is present in the definition of $H'$ we can use a crude upper bound. Given that the dependence is doubly logarithmic the upper bound can be extremely crude. Furthermore, $\delta$ is typically set to be exponentially small, so we ignore this issue.
